---
title: "Tutorial"
output:
  html_document:
    df_print: paged
---

```{r, include = FALSE}
##source("put source here once you figure it out")
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

In this tutorial, we will walk through the application of our proposed algorithm discussed in section 4.1 of the paper. We run the command
```{r}
##test_data <- get_heteroskedastic_gaussian_data(n = 2, 1000, true_mean_vec=rep(0,d), Sigma_max=6, eigensep=3).
```
This returns an $n \times d$ matrix and stores it in the variable `test_data`, and is constructed by taking $n = 1000$ samples from a $d = 2$ dimensional Gaussian distribution, with mean `true_mean_vec` $(0, 0)$  and covariance $\text{diag}(6, 3)$ (a $d \times d$ diagonal matrix with upper-left entry `Sigma_max=6`, and decreasing in increments of `eigensep` until the diagonal is filled). The function `get_heteroskedastic_gaussian_data` is only included for the sake of examples and testing, and in real applications any $n \times d$ matrix can be used as data for the algorithm.

Next, run
```{r} 
##new_estimator <- generate_estimator_with_logcondens(test_data, r = 0.5, plotting = TRUE)
```
This returns a list, consisting respectively of the PCA estimate of the miximg matrix $W$, a list of the $d$ marginal densities $\mathbb{R} \to \mathbb{R}$ of the estimator, and the mean of the estimated distribution.